\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{listings}
\geometry{letterpaper, margin=1in}

\usepackage{minted}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

% Listings setup
\lstset{
    basicstyle=\ttfamily\small,
    frame=single,
    numbers=none,
    tabsize=4,
    showstringspaces=false,
    breaklines=true
}

\begin{document}

\begin{center}
    {\small \textbf{IA Competitive Programming Club}} \\[6pt]
    {\Large Sets \& Maps Worksheet} \\[12pt]
    {\small November 19, 2025}
\end{center}
\vspace{0.5em}

\begin{enumerate}[label=\textbf{\arabic*.}]

    \item Fill in the expected time (average case):
    $$
    \texttt{set.add: } \rule{2.5cm}{0.4pt} \quad
    \texttt{(x in s): } \rule{2.5cm}{0.4pt} \quad
    \texttt{dict lookup: } \rule{2.5cm}{0.4pt}
    $$
    \vspace{0.2cm}

    \item If you declare \texttt{my\_set = \{1, 1, 2, 2, 3\}}, duplicates will be automatically removed. Circle one of the following.
    \begin{center}\textbf{True \quad False}\end{center}

    \item Circle all types that can be dictionary keys: \quad
    \texttt{int \quad str \quad tuple \quad list}
    \vspace{0.5cm}

    \item For a map \texttt{m}, what is the difference between using \texttt{m.get(-)} and \texttt{m[-]}?
    \vspace{0.5cm}

\end{enumerate}

\begin{enumerate}[label=\textbf{\arabic*.}, start=5, itemsep=1cm]

    \item Predict the output:
    \begin{minted}[frame=single,framesep=10pt]{python}
s = set()
for x in [10, 10, 3, 5, 3]:
    s.add(x)
print(len(s))
    \end{minted}
    Output: \rule{3cm}{0.4pt}  

    \item Predict the output:
    \begin{minted}[frame=single,framesep=10pt]{python}
m = {}
m["a"] = 4
m["b"] = 7
m["a"] += 5
print(m["a"], m.get("c", 0))
    \end{minted}
    Output: \rule{4cm}{0.4pt}  

    \item Predict the output:
    \begin{minted}[frame=single,framesep=10pt]{python}
nums = [5,1,5,8,8,8]
freq = {}
for x in nums:
    freq[x] = freq.get(x, 0) + 1
print(freq[5] + freq[8])
    \end{minted}
    Output: \rule{3cm}{0.4pt}  

    \item Predict the output:
    \begin{minted}[frame=single,framesep=10pt]{python}
A = set([2,4,6])
B = set([4,2,6,6])
print(A == B)
    \end{minted}
    Output: \rule{2cm}{0.4pt}  
    \vspace{1cm}

\end{enumerate}

\begin{enumerate}[label=\textbf{\arabic*.}, start=9]

    \item You insert $400{,}000$ distinct numbers into a set.
    There are $10{,}000$ buckets.
    What is the number of expected items per bucket?  
    \vspace{0.5cm}

    \item A dictionary \texttt{freq} stores word counts.
    If the most common word appears $6000$ times and the least appears once, what does the following produce?
    \begin{minted}[frame=single,framesep=10pt]{python}
max(freq.values()) - min(freq.values())
    \end{minted}
    Answer: \rule{3cm}{0.4pt}
    \vspace{0.5cm}

    \item Write a one-line Python expression that prints the smallest value in a dictionary \texttt{price}:  
    \vspace{0.5cm}

    \item A program performs $N$ membership checks on a set of size $N$, and then does the same on a list of the same size.  
    What are the expected total times (in $O$-notation) for the set checks and for the list checks?

\end{enumerate}

\end{document}
