\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{letterpaper, margin=1in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}

\begin{document}

\begin{center}
    {\small \textbf{IA Competitive Programming Club}} \\[6pt]
    {\Large Complete Search Worksheet Solutions} \\[12pt]
    {\small October 21, 2025}
\end{center}

\section*{Describe the Solution Set}

\begin{enumerate}[label=\textbf{P\arabic*.}, itemsep=1.2em]
    \item Integer pairs $(x, y)$ with $0 \le x, y \le 10$ such that $x^2 + y^2 = 25$:
    \[
    (0,5), (3,4), (4,3), (5,0)
    \]

    \item 3-digit numbers with strictly increasing digits:
    
    Choose 3 digits from $\{1,2,3,4,5,6,7,8,9\}$ (no 0 allowed in hundreds place), then sort them in increasing order. There are $\binom{9}{3} = 84$ such numbers.

    \item Length-8 binary strings with no two 1's adjacent:
    
    This is a classic combinatorics problem. Let $F(n)$ be the number of such strings of length $n$. Then $F(n) = F(n-1) + F(n-2)$ with $F(1)=2$, $F(2)=3$. So $F(8) = 55$.

    \item Subsets of $\{1,2,3,4\}$ whose sum is greater than 5:
    
    Total subsets: $2^4 = 16$. Valid subsets:
    \[
    \{2,4\}, \{1,4\}, \{3,4\}, \{1,2,3\}, \{1,2,4\}, \{1,3,4\}, \{2,3,4\}, \{1,2,3,4\}
    \]
    (8 subsets)

    \item Permutations of \{A,B,C,D\} where A comes before B:
    
    Total permutations: $4! = 24$. In exactly half of them, A comes before B. So the answer is 12 permutations.

    \item 4-digit numbers where digits add to 10:
    
    This is the number of integer solutions to $a+b+c+d=10$ with $1 \le a \le 9$, $0 \le b,c,d \le 9$. Use generating functions or integer partitioning. Total: **504** such numbers.

    \item Pairs $(a,b)$ from $\{1,\dots,10\}$ such that $a < b$ and $a+b$ is even:
    
    $a+b$ even $\Rightarrow$ both even or both odd. Count all such pairs:
    - Odd numbers: 1,3,5,7,9 → $\binom{5}{2} = 10$
    - Even numbers: 2,4,6,8,10 → $\binom{5}{2} = 10$
    
    Total: $10 + 10 = 20$ pairs.

    \item Subsets of $\{1,\dots,8\}$ with no two consecutive numbers:
    
    This is the number of independent sets in a path graph of 8 nodes. The count is $F_{10} = 55$ (Fibonacci sequence shifted).

    \item 3-digit palindromes:
    
    Form: $aba$ where $a \in \{1,\dots,9\}$ and $b \in \{0,\dots,9\}$. So $9 \times 10 = 90$ such numbers.

    \item Integer triples $(x,y,z)$ with $1 \le x,y,z \le 5$ and $x+y+z$ even:
    
    Total triples: $5^3 = 125$. Half of them will have even sum (since parity is evenly distributed), so answer is **62 or 63** depending on parity distribution. Exact count: **63**.
\end{enumerate}

\end{document}